\documentclass{article}
\usepackage{verse}

\begin{document}

\poemtitle{The Charge of the Light Brigade}
\settowidth{\versewidth}{Stormed at with shot and shell,}

\newcommand{\attrib}[1]{%
  \nopagebreak{\raggedleft\footnotesize #1\par}}

\begin{verse}[\versewidth]

\flagverse{I}
Half a league, half a league, \\*    
Half a league onward, \\*
All in the valley of Death \\*
\vin Rode the six hundred. \\*
"Forward, the Light Brigade! \\*
Charge for the guns!" he said. \\*
Into the valley of Death \\*
\vin Rode the six hundred. 

\flagverse{II}
"Forward, the Light Brigade!"  \\*
Was there a man dismayed?  \\*
Not though the soldier knew  \\*
\vin Someone had blundered.  \\*
\vin Theirs not to make reply,  \\*
\vin Theirs not to reason why,  \\*
\vin Theirs but to do and die.  \\*
\vin Into the valley of Death  \\*
\vin Rode the six hundred.  

\flagverse{III}
Cannon to right of them,  \\*
Cannon to left of them,  \\*
Cannon in front of them  \\*
\vin Volleyed and thundered;  \\*
Stormed at with shot and shell,  \\*
Boldly they rode and well,  \\*
Into the jaws of Death,  \\*
Into the mouth of hell  \\*
\vin Rode the six hundred.

\flagverse{IV}
Flashed all their sabres bare,  \\*
Flashed as they turned to air  \\*
Sabring the gunners there, \\*
Charging an army, while \\*
\vin All the world wondered. \\*
Plunged in the battery-smoke \\*
Right through the line they broke; \\*
Cossak and Russian \\*
Reeled from the sabre stroke \\*
\vin Shattered and sundered. \\*
Then they rode back, but not \\*
\vin Not the six hundred.

\flagverse{V}
Cannon to right of them, \\*
Cannon to left of them, \\*
Cannon behind them \\*
\vin Volleyed and thundered; \\*
Stormed at with shot and shell, \\*
While horse and hero fell. \\*
They that had fought so well \\*
Came through the jaws of Death, \\*
Back from the mouth of hell, \\*
All that was left of them, \\*
\vin Left of six hundred. 

\flagverse{VI}
When can their glory fade? \\*
O the wild charge they made! \\*
\vin All the world wondered. \\*
Honour the charge they made! \\*
Honour the Light Brigade, \\*
\vin Noble six hundred!

\end{verse}

\attrib{Alfred, Lord Tennyson (1809-1892)}

\end{document}
